### 2022-01-25 manuscript/manuscript.Rmd
Finish the methods section

>>>>

The quality of the models was then evaluated both numerically and graphically. The numerical assessment was made by computing the following accuracy indices: the mean absolute error (MAE), mean absolute percent error (MAPE) and root mean square error (RMSE). To visualize the agreement between the values predicted by the models and measured by the FP, Bland-Altman plots were drawn. This type of plot is made by plotting the mean of the actual and predicted values on the x axis and their difference on the y axis. Then, the bias was calculated as the mean of these differences and plotted as a continuous horizontal line, and the limits of agreement were defined by bias ± 1.96 standard deviation and plotted as horizontal dashed lines [@Bland1986]. To further test if there were any consistent under- or over-estimation of the values by the models, one-sample *t*-tests were done to check whether the bias were different than zero. Finally, linear regressions were employed to examine if the difference between actual and predicted values were affected by their magnitude, verifying, therefore, whether the prediction was constant throughout the magnitude range that was tested [@Giavarina2015].
